---
header-includes:
    - \usepackage{fancyhdr}
    - \fancyfoot[CO,CE]{OSC-Group - http://www.osc-lab.de - JMU Wuerzburg - Pharmazie}
    - \fancyfoot[LE,RO]{\thepage}
    - \usepackage{fontspec}
    - \setmainfont{OpenSans}
    - \usepackage{lscape}
    - \newcommand{\blandscape}{\begin{landscape}}
    - \newcommand{\elandscape}{\end{landscape}}
    
title: "TDM Report - SimKi"
output: 
  pdf_document:
    latexengine: xelatex
df_print: paged
date: "`r format(Sys.time(), '%d.%B %Y')`"


---
\setmainfont{OpenSans}
\addtolength{\headheight}{1.0cm} 
\pagestyle{fancyplain} 
\rhead{\includegraphics[height=1.2cm]{./logo_rechts.jpg}} 
\lhead{\includegraphics[height=1.2cm]{./logo_links.png}}
\renewcommand{\headrulewidth}{0pt}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Patient characteristics**

Current treatment: **`r MODEL_FILES[as.numeric(input$SELECT_DRUG)]`**
  
Patient ID: **`r input$pat_ID`** 
  
Body weight: **`r input$WT`** kg 

Sex: **`r input$SEX``**

Age: **`r input$AGE`** years

Other covariates used:

``` {r tdm_cov, echo=FALSE, warning=FALSE}

kable(app_data$cov_table, format = "latex")  %>%
    kable_styling(position = "left")

```


# **Clinical Recommendation**

``` {r clin_eval, echo=FALSE, warning=FALSE}

for(i in 1:length(app_data$clinical_eval)) {
  print(app_data$clinical_eval[i])
  print("\n")
}

```

## **Custom dosing**
``` {r custom_dosing, echo=FALSE, warning=FALSE}

rep_temp_custom <- app_data$custom_scheme_data
colnames(rep_temp_custom) = c("Dose [mg]", "Interval [h]", 
                     "Steady State Cmin [ng/mL]", 
                     "Steady State AUC (tau) [ng/mL h]")
kable(rep_temp_custom, 
      format = "latex")  %>%
    kable_styling(position = "left")

```

## **Other predefined schemes**
``` {r predefined_dosing, echo=FALSE, warning=FALSE}

rep_temp_custom <- app_data$scheme_data
colnames(rep_temp_custom) = c("Dose [mg]", "Interval [h]", 
                     "Steady State Cmin [ng/mL]", 
                     "Steady State AUC (tau) [ng/mL h]")
kable(rep_temp_custom, 
      format = "latex")  %>%
    kable_styling(position = "left")

```

\newpage

# **Dataset used**

## **Dosing data**
``` {r tdm_dosing, echo=FALSE, warning=FALSE}

tmp_rep_data <- app_data$user_data_set %>% filter(`EVID`==1)
colnames(tmp_rep_data) = c("Date", "Time", "Dose [mg]", "Conc [ng/mL]", "Event ID")
kable(tmp_rep_data, 
      format = "latex")  %>%
    kable_styling(position = "left")

```

## **Measured concentrations data**
``` {r tdm_conc, echo=FALSE, warning=FALSE}

tmp_rep_data <- app_data$user_data_set %>% filter(`EVID`==0)
colnames(tmp_rep_data) = c("Date", "Time", "Dose [mg]", "Conc [ng/mL]", "Event ID")
kable(tmp_rep_data, 
      format = "latex")  %>%
    kable_styling(position = "left")

```


\newpage
\blandscape

# **Simulated Plasmaconcentration from Dataset**


```{r simulation, echo=FALSE, warning=FALSE, fig.height = 7, fig.width = 12, fig.align = "center"}
if(!is.null(app_data$current_plot)){
  app_data$current_plot
}

```

\elandscape